Ms 1

### 2017-08-18 ms1/ms1_display.Rmd
ms1 raw trends

```{r adjusted_changes}
x = model_abx %>%
  filter(term=='year0') %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  arrange(pct_change) %>%
  mutate(antibiotic=fct_inorder(antibiotic),
         antibiotic=fct_relevel(antibiotic, 'overall', after=Inf))

x %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted yearly change in consumption (%)') +
  scale_y_continuous(limits=c(-10, 10), breaks=c(-10, -5, 0, 5, 10)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

>>>>

```{r adjusted_changes}
adjusted_changes = model_abx %>%
  filter(term=='year0') %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  arrange(pct_change) %>%
  mutate(antibiotic=fct_inorder(antibiotic),
         antibiotic=fct_relevel(antibiotic, 'overall', after=Inf))

unadjusted_changes = bind_rows(claims_by_abx, claims_overall) %>%
  filter(antibiotic %in% c('overall', top_abx), year %in% c(2011, 2014)) %>%
  select(antibiotic, year, cpkp) %>%
  spread(year, cpkp) %>%
  mutate(change=(`2014`-`2011`)/3,
         fold_change=change/`2011`,
         pct_change=100*fold_change) %>%
  select(antibiotic, pct_change)

adjusted_changes %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  geom_point(dat=unadjusted_changes, aes(x=antibiotic, y=pct_change, ymin=NULL, ymax=NULL), color='red') +
  coord_flip() +
  xlab('') +
  ylab('adjusted yearly change in consumption (%)') +
  scale_y_continuous(limits=c(-10, 10), breaks=c(-10, -5, 0, 5, 10)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```
